Bioverse: Exoplanet Biosignature Detection Under the UV Threshold Hypothesis

### 2024-09-26 src/tex/ms.tex
draft a title
highlight M dwarfs in Results

% Title
\title{Bioverse: Origins of Life}

@@

\subsection{Survey simulations with Bioverse}\label{sec:results-bioverse}
%\begin{figure}
%    \script{inhabited_FGKM.py}
%    \begin{centering}
%        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
%        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
%        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
%        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
%        }
%        \label{fig:inhabited_FGKM}
%    \end{centering}
%\end{figure}
In a magnitude- and volume-limited sample of a transit survey, the host star distribution for \glspl{EEC} will be skewed toward later spectral types and dominated by M~dwarfs due to how the \gls{HZ} scales with spectral type.
For a fixed planet sample size, the fraction of inhabited planets is highest in the M~dwarf sample due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars (see Figure~\ref{fig:surveys_FGKM}).
Their \gls{NUV} fluxes are generally highest at early times $\lesssim\SI{100}{\mega\year}$.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (compare Equation~\ref{eq:hypothesis-uv}).
%Because of that, most inhabited planets in our magnitude- and volume-limited sample orbit M~dwarfs.

>>>>

% Title
\title{Bioverse: Exoplanet Biosignature Detection Under the UV Threshold Hypothesis}
% The Role of Ultraviolet Radiation in Abiogenesis: Insights from Exoplanet Survey Simulations
% Bioverse: The Impact of UV Flux on Exoplanet Biosignatures under the Cyanosulfidic Origins of Life Scenario

@@

\subsection{Survey simulations with Bioverse}\label{sec:results-bioverse}
%\begin{figure}
%    \script{inhabited_FGKM.py}
%    \begin{centering}
%        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
%        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets in a simulated transit survey.
%        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
%        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
%        }
%        \label{fig:inhabited_FGKM}
%    \end{centering}
%\end{figure}
In a magnitude- and volume-limited sample of a transit survey, the host star distribution for \glspl{EEC} will be skewed toward later spectral types and dominated by M~dwarfs due to how the \gls{HZ} scales with spectral type.
For a fixed planet sample size, the fraction of inhabited planets is highest in the M~dwarf sample due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars (see Figures~\ref{fig:hz_nuv_evo}, \ref{fig:surveys_FGKM}).
Their \gls{NUV} fluxes are generally highest at early times $\lesssim\SI{100}{\mega\year}$.
These host stars, in particular late subtypes, also provide extended periods of increased \gls{NUV} emission that overlap with times when some of these planets occupy the \gls{HZ} (see Figure~\ref{fig:hz_nuv_evo}), our requirement for abiogenesis (compare Equation~\ref{eq:hypothesis-uv}).
Thus -- under the UV Threshold Hypothesis, most inhabited transiting planets in a magnitude- and volume-limited sample orbit M~dwarfs.
